Digital Analysis of Paintings

### 2014-03-31 paper.tex
Add some content to the survey paper.

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
\title{Something to do with Image Processing}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The abstract goes here.
\end{abstract}

@@

\section{Introduction}
% no \IEEEPARstart

\section{Conclusion}
The conclusion goes here.

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{bibliography}

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
\title{Digital Analysis of Paintings}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
%TODO Write this once the paper is complete
\end{abstract}

@@

\section{Introduction}
Digital image processing is a field which encourages the crossover of different
scientific disciplines, often biological research and computer vision align to
automate the collection and analysis of plant growth. However, art and
computing are fields which, at first glance, have very little in common.

But a deeper look unveils a plethora of different avenues from detecting
forgeries to being able to date an artists work within a catalogue of their
known pieces\cite{brown2013can}.

This survey paper will unearth some of the techniques which are used to perform
such analysis and evaluate their application in real world problems.

%TODO this still need some expansion.

\section{Image Processing}
A typical digital image is represented as a matrix of pixels where each pixel
contains information about the colour it represents. This colour can be
described using several different representations and although each
representation will equate to the same colour in the rendered image, the
information stored can be radically different.

This representation of an image provides several key pieces of information,
including:

\begin{itemize}
\item colour space of the image
\item the relationship between pixels
\end{itemize}

The digital processing of images is normally done through the application of
functions or filters to the matrix to gather specific information relating to
the desired result. A simple example of this would be averaging the colours of
an image to get a basic idea of the colours in an image.

More advanced techniques involve performing several of these operations in
sequence to provide a more complex view of the image.

There are many sections of image processing, each with their different purposes
this report will particularly focus on those relating to colour space; edge
detection and orientation for texture analysis and segmentation and regions of
interest for brush stroke analysis.

% TODO write more here too

\section{Colour Space Analysis}

\section{Texture Analysis}

\section{Brush Stroke Analysis}

\section{Application of Image Processing to Artwork}

\subsection{Dating Artists Work}

\section{Conclusion}

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{bibliography}
